\chapter{History}

\emph{''Do you remember the times?''}

Michael Jackson asked this question once.
\piccbc

\newpage
A detailed version is in the Readme.pdf.
\begin{itemize}
  \item 2007-07-07 Code Beautifier Collection 6.0.0.1014 (GrapeVine)
  \begin{enumerate}
    \item + Vista look and feel and task dialog is used wherever suitable.
    \item + Vista UAC compliant.
    \item * Installation experience is improved.
    \item + Object Pascal code style editor is added.
    \item * All bugs reported to Google Code homepage are fixed.
  \end{enumerate}
    \item 2007-03-07 Code Beautifier Collection 5.3.3.1005 (HardQuery Release 2
  Update 3)
  \begin{enumerate}
    \item * Code DOM related bugs are fixed.
    \item + Typing Speeder's support for C\# XML comments.
    \item + Icon Browser feature is added.
    \item + Line Counter feature is added.
    \item * Plus loading bug is fixed.
  \end{enumerate}
  \item 2007-02-10 Code Beautifier Collection 5.3.2.1125 (HardQuery Release 2
  Update 2)
  \begin{enumerate}
  \item * File Aid Dialog is redone.
  \item + InDate Error Dialog is added.
  \item * Bug \#39 is fixed.
  \item * Doc Preview Dialog is updated.
  \item * AutoComplete feature is redone.
  \item * Source Navigator Dialog is updated.
  \item * AutoActivate function in ProjectAid feature is enhanced.
  \item * AutoUpdate function in InDate feature is enhanced.
\end{enumerate}
  \item 2006-12-09 Code Beautifier Collection 5.3.1.1124 (HardQuery Release 2
  Update 1)
    \begin{enumerate}
      \item + Add Lextm Logging Service unit based on log4net.
      \item - MarcClifton's Debug unit is removed.
      \item * NDoc project is replaced by a Sandcastle project.
      \item * JCF 2.25 is used.
      \item + An easter egg is added.
      \item + MSBuild and MSBee are used in the build process.
      \item + InDate UI is changed to a compact one.
      \item + Source Navigator is enhanced.
      \item * Two bugs, \#36 and 37, are fixed.
      \item * All documents are updated.
    \end{enumerate}

  \item 2006-10-21 Code Beautifier Collection 5.3.0.1123 (HardQuery Release 2)
    \begin{enumerate}
      \item + LeXDK Property Registry and Serialization Service.
      \item - Preferences Service is removed.
      \item + ProjectActivator and Source Navigator feature added in WiseEditor.
      \item + Unhandled exceptions can all be caught.
      \item + Rest of ArtCSB and Sharp Builder Tools features are added.
      \item + Clearer, DILMerge, and ProcessChecker are bundled.
      \item * All documents are updated.
    \end{enumerate}
  \item 2006-09-16 Code Beautifier Collection 5.2.0.1123 (HardQuery)
	\begin{enumerate}
	\item * LeXDK core refinements.
	\item * WiseEditor Plus is now version 1.0.
	\item * C\#BuilderGoodies Plus is now version 1.0.
	\item * AddMany Plus is now version 1.0.
	\item + Readme feature added in WiseEditor Plus.
	\item + NFamily Plus Beta is included, default disabled.
	\item + ArtCSB Plus Beta is included, default enabled.
	\item * Bug 24(Doc Preview), 25(Preferences), 26(Format Document), 32(Console
	Project), 33(Plus Manager) are fixed.
	\item + Undo support is added in CodeBeautifiers Plus.
	\item * .feature files are replaced by .ota files.
	\item * Documents are updated.
    \end{enumerate}

\item 2006-7-2 Code Beautifier Collection 5.1.1.1117 (NixNewNer Update 1)
	\begin{enumerate}
	\item + .plus2 file format is added.
	\item - .plus support is removed.
	\item + plus2plus2 tool is included (source code only).
	\item + Multi-level tab in Preferences Dialog is added.
	\item + A CB Plus General Tab is added to add some useful options.
	\item - FileWizards is disabled under BDS 1.0.
	\item + Auto-Update feature called InDate is done.
	\item * Bug 14 and 15 are fixed.
	\item * License.pdf is updated.
	\end{enumerate}

\item 2006-6-8 Code Beautifier Collection 5.1.0.1117 (NixNewNer)
	\begin{enumerate}
	\item * Plus Manager GUI is updated. Use TreeView instead of ListView.
	\item * AutoCompletion is tuned again.
	\item + Adds some XML tag supports in C\# that you can invoke in Ctrl + J. (BDS 4 only)
	\item * \#13 bug on the bug tracker is fixed.
	\item - Input Helper is disabled.
	\item * AddMany Plus now works well under BDS 1.0.
	\item - FileWizards of WiseEditor Plus is disabled under BDS 1.0.
	\item * Documents are updated.
	\end{enumerate}

\item 2006-5-31 Code Beautifier Collection 5.0.2.1018 (WalkPace Update 2)
	\begin{enumerate}
	\item * The icon for LeXtudio is changed.
	\item + Tip of the Day feature is added in Utilities Plus.
	\item + A basic Input Helper feature is added in C\#Builder Goodies Plus and its original Doc Insight is disabled.
	\item + A Wise Editor Plus is added.
	\item * New NANT build file and bat file.
	\item * Documents are updated.
	\end{enumerate}

\item 2006-4-27 Code Beautifier Collection 5.0.1 (WalkPace Update 1)
	\begin{enumerate}
	\item + Utilities Plus (codenamed FunSide) added: Expert Manager and Plus Manager.
	\item * Code Beautifiers Plus codenamed LongJeans added, AStyle calling improved.
	\item + ThirdParty assembly added.
	\item * Classes and methods changes in LeXDK.
	\item * New NANT build file and bat file.
	\item + Mix for BDS (a few useful menu shortcuts) added.
	\item * New installer.
	\item * Licensing changed. See license.pdf.
	\item * Documentation updated.
	\end{enumerate}

\item 2006-3-16 Code Beautifier Collection 5.0 (WalkPace)
	\begin{enumerate}
	\item * Bugs fixed and more refactoring.
	\item + LeXDK is ready.
	\item + First Plus Pack is ready.
	\item * Docs are updated completely for the second time.
	\end{enumerate}

\item 2006-2-12 Code Beautifier Collection 4.3 (BigFace)
	\begin{enumerate}
	\item * Bugs fixed and more refactorings.
	\end{enumerate}

\item 2005-12-25 Code Beautifier Collection Expert v2.4 Beta 2
	\begin{enumerate}
	\item + Add basic user-defined JCF style support.
	\item * Bugs fixed and more refactorings.
	\end{enumerate}

\item 2005.12.10 Code Beautifier Collection Expert v2.4 Beta 1
	\begin{enumerate}
	\item * support BDS 2006.
	\item * Bugs fixed and more refactorings.
	\end{enumerate}

\item 2005.11.18 Code Beautifier Collection Expert v2.2
	\begin{enumerate}
	\item * Bugs fixed and more refactorings.
	\end{enumerate}

\item 2005.10.15 Code Beautifier Collection Expert v2.1 for Delphi 2005
	\begin{enumerate}
	\item * Refactor to SBT v3.1.0.0 architecture compatible, and import some ArtCSB's functions.
	\item + ''Project'' and ''Project Group'' menu items are added. But they are usually unsafe and a lot of further tests are in my list.
	\item + An option of shortcut is added. Now you can change the shortcut to whatever you like.
	\item + An option of CBC menu position is added.
	\end{enumerate}

\item 2005.6.18 Code Beautifier Collection Expert v2.0 for Delphi 2005
	\begin{enumerate}
	\item * Update to Delphi 2005 Update 3 compatible.
	\item + Rename to Code Beautifier Collection Expert, since AStyle interface is added.
	\end{enumerate}

\item 2005.3.17 JCFExpert v1.0.1
	\begin{enumerate}
	\item * Update to Delphi 2005 Update 2 compatible.
	\end{enumerate}

\item 2005.3.16 JEDI Code Format Integration Expert v1.0.(0) for Delphi 2005
	\begin{enumerate}
	\item + Add simplest feature for Jcf.exe.
	\item + Initial stable version to public.
	\end{enumerate}

\end{itemize}
